TrenchR: an R package for transparent environmental and ecological biophysics

### 2022-06-14 ManuscriptTe.Rmd
very minor fix

---
title: "Appendix S1"
author: "Buckley et al."
output:
  word_document: default
  pdf_document: default
  html_document: default
  rmarkdown::html_vignette: default
---

@@

We then implement the energy budget as follows.
```{r echo=T, results = 'hide', warning=FALSE}
TeGates= rep(NA, nrow(dat) )

>>>>

---
title: "Appendix S1"
author: "Buckley et al."
output:
  html_document: default
  pdf_document: default
  word_document: default
  rmarkdown::html_vignette: default
---

@@

We then implement the energy budget as follows. We note that the energy budget can not be solved for some time periods and errors are generated.
```{r echo=T, results = 'hide', warning=FALSE}
TeGates= rep(NA, nrow(dat) )

### 2022-06-14 Manuscript_full.Rmd
very minor fix

---
title: 'TrenchR: an R package for transparent environmental and ecological biophysics'
author: "Lauren B. Buckley, Bryan A. Briones Ortiz, Isaac Caruso, Aji John, Ofir Levy, Abigail V. Meyer, Eric A. Riddell, Yutaro Sakairi, and Juniper Simonis"
output:
  word_document: default
  html_document: default
  pdf_document: default
bibliography: bibliography.bib
csl: methods-in-ecology-and-evolution.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

#add additional axis with radiation
par(new = T)
plot(1:24, Sdir, pch=16, axes=F, xlab=NA, ylab=NA, type="l", col="#FDE725FF")
axis(side = 4)
mtext(side = 4, line = 3, 'Radiation (W/m^2)')
legend("topleft",
       legend=c("Ta (2m)", "Ta (0.02m)", "Ts", "Te", "Radiation"),
       lty=1, pch=NA, col=c("#440154FF", "#3B528BFF", "#21908CFF", "#5DC863FF", "#FDE725FF"))

>>>>

---
title: 'TrenchR: an R package for transparent environmental and ecological biophysics'
author: "Lauren B. Buckley, Bryan A. Briones Ortiz, Isaac Caruso, Aji John, Ofir Levy, Abigail V. Meyer, Eric A. Riddell, Yutaro Sakairi, and Juniper Simonis"
output:
  html_document: default
  word_document: default
  pdf_document: default
bibliography: bibliography.bib
csl: methods-in-ecology-and-evolution.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

#add additional axis with radiation
par(new = T)
plot(1:24, Sdir, pch=16, axes=F, xlab=NA, ylab=NA, type="l", col="#FDE725FF")
axis(side = 4)
mtext(side = 4, line = 3, 'Radiation (W/m^2)')
legend("topleft",
       legend=c("Ta (2m)", "Ta (0.02m)", "Ts", "Te", "Radiation"),
       lty=1, pch=NA, col=c("#440154FF", "#3B528BFF", "#21908CFF", "#5DC863FF", "#FDE725FF"))
```
